### 2014-07-23 fundamentals/intro.tex
adding helpful guiding comments
actual ntmanuscript class
adds draft topic sentences to intro.

% Why did we do the work?
% What were the central motivations and hypotheses?
% The objectives of the work.
% What will this work show
% Why is it important?
% What should the reader watch for in the paper?
% What are the interesting high points?
% What strategy did we use?
% What should the reader expect as conclusion?

@@

\subsection{Motivation}
\subsubsection{Modular Architecture}
% Motivation for encapsulated plug-in architecture 
% enables ecosystem, ease of contribution across institutions
% enables myriad levels of simulation fidelity
% enables FC analyses that can compare ‘apples to apples'
\subsubsection{Agent-based Paradigm}
% superior detail in capturing simulation dynamics
% more flexible control over behavior
% describe Region/Institution/Facility hierarchy
% note importance of generic resource exchange paradigm
\subsubsection{Discrete Resource Tracking}
% enables more realistic models and metrics
% material routing metrics
% shadow fuel cycles
% etc.

>>>>

% Why did we do the work?
% What were the central motivations and hypotheses?
% The objectives of the work?
% What will this work show the reader?
% Why is it important?
% What should the reader watch for in the paper?
% What are the interesting high points?
% What strategy did we use?
% What should the reader expect as conclusion?

In nuclear fuel cycle simulation it is necessary to calculate and optimize 
nuclear process physics, facility deployment, material routing, etc.

Historically, nuclear fuel cycle simulators have addressed this with software 
ranging from spreadsheet driven flow calculators to full detail industrial 
models.

An alternative to these approaches is a dynamic, agent-based simulator with an 
open platform.

@@

Simulators drive R\&D by calculating metrics that can be compared accross fuel 
cycles.

Previous simulators have been static or dynamic. Some have been discrete while 
others have been fleet-based. Some have captured regional behavior, material 
isotopics, transmutation detail, etc. Indeed, some tools have attempted 
agent-based functionality.

Historically, the national laboratories have driven development and regulated 
the use of their own tools (cite VISION, DANESS, NFCSim, etc.), while 
universities and industry have simultaneously developed tools of their own as 
well.

The Cyclus code arose out of the GENIUSv2 code. That software itself was the 
result of lessons-learned from an LDRD project at INL called GENIUSv1.

\subsection{Motivation}
% Gently reiterate the above need. 
% There should be a hero narrative here
% There was a gap in the capabilities of simulators.
% Cyclus, a hero, came in to fill that gap.

Cyclus provides a sophisticated and modern, agent-based platform. Previous 
codes were lacking in a number of ways. Cyclus has a number of features that 
overcome those issues.

\subsubsection{Modular Architecture}
% Motivation for encapsulated plug-in architecture 
% enables ecosystem, ease of contribution across institutions
% enables myriad levels of simulation fidelity
% enables FC analyses that can compare ‘apples to apples'

Draw from and cite the ``Open Architecture and Modular Paradigm'' ANS summary.

\subsubsection{Agent-based Paradigm}
% superior detail in capturing simulation dynamics
% more flexible control over behavior
% describe Region/Institution/Facility hierarchy
% note importance of generic resource exchange paradigm

ABM is modern, sophisticated, true to reality, and it takes advantage of modern 
computing resources.

\subsubsection{Discrete Resource Tracking}
% enables more realistic models and metrics
% material routing metrics
% shadow fuel cycles
% etc.

Not all simulations can be successfully run with a fleet-based model that 
doesn't distinguish between discrete materials. Shadow fuel cycles are an 
example.
